Centers and centralizers of higher enveloping algebras of Lie algebras

### 2020-10-21 draft.tex
added small reminders about my confusions
attempt at spec seq construction

\subsection{Deformations of $\EE_n$ enveloping algebras}
It is well-known that the Hochschild cohomology of an associative, or $\EE_1$-algebra, controls its deformations. 
Precisely, if $A$ is an $\EE_1$-algebra then the shift of its Hochschild cohomology ${\rm Hoch}^\bu (A , A)[1]$ carries a Lie algebra structure (in the homotopical sense). 
The Maurer--Cartan elements of this dg Lie algebra classify deformations of $A$ as an $\EE_1$-algebra.

Similarly, if $A$ is an $\EE_n$-algebra, the $\EE_n$-center $\fZ_n(A)$ controls deformations of $A$ as $\EE_n$-algebra. 
Since $\fZ_n(A)$ is an $\EE_{n+1}$-algebra, the shift $\fZ_n(A)[n]$ is equipped with a Lie bracket. 
Maurer--Cartan elements classify deformations of $A$ as an $\EE_{n}$-algebra.

Using our model for the $\EE_n$-center, we obtain an explicit description 
of deformations of $\EE_n$-enveloping algebras.

\begin{prp}\label{prop:def}
There is a canonical quasi-isomorphism 
\begin{equation}\label{eqn:def}
\bZ_n(\UU_n \fg) \xto{\simeq} \clies\left(\fg, \Sym(\fg[1-n]) \right) .
\end{equation}
%In particular, the cochain complex on the right-hand side has the structure of an $\EE_{n+1}$ algebra. 
In particular, $\EE_n$-deformations of $\UU_n \fg$ up to equivalence are in bijective correspondence with the cohomology group
\[
H^{n+1} \bigg(\clie^\bu \left(\fg , \Sym(\fg[1-n]) \right) \bigg).
\]
\end{prp}
\begin{proof}
The first statement follows from the Poincar\'{e} lemma for de Rham forms and compactly supported de Rham forms
\[
\bZ_n(\UU_n \fg) = \clie^\bu\left(\Omega^\bu(\RR^n) \otimes \fg, \clieu_\bu(\Omega^\bu_c (\RR^n) \otimes \fg\right) \xto{\simeq} \clies\left(\fg, \Sym(\fg[1-n]) \right) .
\]
The second statement follows from the fact that Maurer--Cartan elements in $\bZ_n(\UU_n \fg)[n]$ classify deformations of $\UU_n \fg$. 
\end{proof}

\begin{rmk}
When $n=1$ the quasi-isomorphism of the above proposition produces the well-known quasi-isomorphism
\[
{\rm Hoch}^\bu(U \fg , U \fg) \simeq \clie^\bu(\fg , \Sym(\fg)) ,
\]
see \cite{LodayCyclicBook}. 
\end{rmk}

%As a corollary of the above proposition, we obtain a concrete description for $\EE_n$-deformations of $\UU_n \fg$ when $\fg$ is an ordinary (strict) Lie algebra. 
Suppose $\fg$ is an ordinary Lie algebra.
It is known that if $\fg$ is semi-simple then the $\EE_1$-enveloping algebra $\UU_1 \fg$ is rigid in the sense that it admits no nontrivial deformations. 
This follows from the above equivalence (\ref{eqn:def}) together with the fact that $H_{\rm Lie}^2(\fg , \Sym(\fg)) = 0$ when $\fg$ is semi-simple by Whitehead's theorem.

@@

\owen{I've gotten myself pretty mixed up about this \dots It's fixable but I need to think things through.}

@@

>>>>

\subsection{Deformations of enveloping $\EE_n$ algebras}
It is well-known that the Hochschild cohomology of an associative, or $\EE_1$ algebra, controls its deformations. 
Precisely, if $A$ is an $\EE_1$ algebra then the shift of its Hochschild cohomology ${\rm Hoch}^\bu (A , A)[1]$ carries a Lie algebra structure (in the homotopical sense). 
The Maurer--Cartan elements of this dg Lie algebra classify deformations of $A$ as an $\EE_1$ algebra.

Similarly, if $A$ is an $\EE_n$ algebra, the $\EE_n$ center $\fZ_n(A)$ controls deformations of $A$ as $\EE_n$-algebra. 
Since $\fZ_n(A)$ is an $\EE_{n+1}$ algebra, the shift $\fZ_n(A)[n]$ is equipped with a Lie bracket. 
Maurer--Cartan elements classify deformations of $A$ as an $\EE_{n}$ algebra.

Using our model for the $\EE_n$ center, we obtain an explicit description 
of deformations of $\EE_n$ enveloping algebras.

\begin{prp}\label{prop:def}
There is a canonical quasi-isomorphism 
\begin{equation}
\label{eqn:def}
\bZ_n(\UU_n \fg) \xto{\simeq} \clies\left(\fg, \Sym(\fg[1-n]) \right) .
\end{equation}
%In particular, the cochain complex on the right-hand side has the structure of an $\EE_{n+1}$ algebra. 
In particular, $\EE_n$-deformations of $\UU_n \fg$ up to equivalence are in bijective correspondence with the cohomology group
\[
H^{n+1} \bigg(\clie^\bu \left(\fg , \Sym(\fg[1-n]) \right) \bigg).
\]
\end{prp}
\begin{proof}
The first statement follows from the Poincar\'{e} lemma for de Rham forms and compactly supported de Rham forms
\[
\bZ_n(\UU_n \fg) = \clie^\bu\left(\Omega^\bu(\RR^n) \otimes \fg, \clieu_\bu(\Omega^\bu_c (\RR^n) \otimes \fg\right) \xto{\simeq} \clies\left(\fg, \Sym(\fg[1-n]) \right) .
\]
The second statement follows from the fact that Maurer--Cartan elements in $\bZ_n(\UU_n \fg)[n]$ classify deformations of $\UU_n \fg$. 
\end{proof}

When $n=1$ the quasi-isomorphism of the above proposition produces the well-known quasi-isomorphism
\[
{\rm Hoch}^\bu(U \fg , U \fg) \simeq \clie^\bu(\fg , \Sym(\fg)).
\]
See~\cite{LodayCyclicBook} for discussion of Hochschild (co)homology for such ``almost commutative'' algebras.

%As a corollary of the above proposition, we obtain a concrete description for $\EE_n$-deformations of $\UU_n \fg$ when $\fg$ is an ordinary (strict) Lie algebra. 
Consider the situation of an ordinary Lie algebra~$\fg$.
When $\fg$ is semi-simple, the enveloping $\EE_1$ algebra $\UU_1 \fg$ is rigid in the sense that it admits no nontrivial deformations. 
This claim follows from the above equivalence (\ref{eqn:def}) together with the fact that $H_{\rm Lie}^2(\fg , \Sym(\fg)) = 0$ for $\fg$ is semi-simple by Whitehead's theorem.

@@

\owen{I've gotten myself pretty mixed up about this \dots too many duals with infinite dimensional vector spaces, and issues with whether you can base-change a semi-free algebra.}

@@

The left hand side is eminently computable, 
amounting to a computing relative de Rham cohomology.
What we really want is a convenient model for the entire factorization algebra whose behavior recovers the pair $(\Gr \frak{Z}_n(\fg), \Gr \UU_n \fg)$.
Thankfully, it is straightforward to find one, via classic algebraic topology.

For any open subset $V$ in $M$, define
\[
\Omega^*_{{\rm rel }}(V) = \{ \alpha \in \Omega^*(V) \, : \, \alpha|_{\partial M} = 0\}.
\]
This construction models cohomology relative to the boundary.
Note that
\[
\Omega^*_{{\rm rel }}(U \times [0,\epsilon)) \simeq \Omega^*)_U \otimes \Omega^*_{{\rm rel }}([0,\epsilon)) \simeq 0
\]
as the relative cochains $\Omega^*_{{\rm rel }}([0,\epsilon))$ are acyclic.

Consider the prefactorization algebra on $M$ that assigns to the open set $V$, 
the cochain complex
\[
F_{{\rm rel}}(V) =\clies(\Omega^*_{{\rm rel }}(V) \otimes \fg, \Sym(\Omega^*_c(V) \otimes \fg[2])).
\]
When $V$ is an open set inside $\mathring{M}$, we find $F_{{\rm rel}}(\mathring{M})$ agrees with  $\Gr \frak{Z}_n(\fg)(V)$.
When $V$ is a product open $U \times [0,\epsilon)$ along the boundary, we find 
\[
F_{{\rm rel}}(V) \simeq \clies(0, \Sym(\Omega^*_c(U) \otimes \fg[1])) \simeq \Sym(\Omega^*_c(U) \otimes \fg[1]) \simeq \Gr \UU_n \fg(U),
\]
as desired.
\owen{Maybe in the second factor I replace $V$ by $V \setminus (V \cap \partial M)$?}
This construction $F_{{\rm rel}}$ defines, in fact, a factorization algebra by a mild variant of the argument from \owen{cite GRW}.

We thus find
\[
\int_{(M,\partial M)} (\Gr \frak{Z}_n(\fg), \Gr \UU_n \fg) \simeq F_{{\rm rel}}(M) =\clies(\Omega^*_{{\rm rel }}(M) \otimes \fg, \Sym(\Omega^*_c(\mathring{M}) \otimes \fg[2])).
\]
Let us now focus on the case where $M$ is compact with boundary.
Then $\Omega^*_c(\mathring{M}) = \Omega^*_{{\rm rel}}(M)$, so
\[
\int_{(M,\partial M)} (\Gr \frak{Z}_n(\fg), \Gr \UU_n \fg) 
\simeq \clies(\Omega^*_{{\rm rel }}(M) \otimes \fg, \Sym(\Omega^*_{{\rm rel}}(M) \otimes \fg[2])),
\]
and so it remains to compute relative cohomology.

\owen{revisit and revise}

%By definition~\ref{dfn:constructible1}, we have a model for the pair $(\Gr \frak{Z}_n(\fg), \Gr \UU_n \fg)$.
%To see this, observe that to an open subset $V$ of the interior $\mathring{M}$, 
%the factorization algebra assigns
%\begin{equation}
%\label{eqn: gr Z}
%\clies(\Omega^*(V) \otimes \fg, \Sym(\Omega^*_c(V) \otimes \fg[2])).
%\end{equation}
%Given an open set $U \subset \partial M$ and a small open neighborhood in $M$ of $U$ such as $U \times [0,\epsilon)$ (depending on a choice of local collar coordinate), 
%the factorization algebra assigns
%\[
%\Sym(\Omega^*_c(U)\otimes \fg[1]),
%\]
%up to quasi-isomorphism.
%
%What we really want is a convenient model for this entire factorization algebra whose behavior recovers with the values above.
%Thankfully, it is straightforward to find one, via classic algebraic topology.
%For any open subset $V$ in $M$, define
%\[
%\Omega^*_{{\rm rel }}(V) = \{ \alpha \in \Omega^*(V) \, : \, \alpha|_{\partial M} = 0\}.
%\]
%This construction models cohomology relative to the boundary.
%Note that
%\[
%\Omega^*_{{\rm rel }}(U \times [0,\epsilon)) \simeq \Omega^*)_U \otimes \Omega^*_{{\rm rel }}([0,\epsilon)) \simeq 0
%\]
%as the relative cochains $\Omega^*_{{\rm rel }}([0,\epsilon))$ are acyclic.
%
%Consider the prefactorization algebra on $M$ that assigns to the open set $V$, 
%the cochain complex
%\[
%F_{{\rm rel}}(V) =\clies(\Omega^*_{{\rm rel }}(V) \otimes \fg, \Sym(\Omega^*_c(V) \otimes \fg[2])).
%\]
%When $V$ is an open set inside $\mathring{M}$, we find $F_{{\rm rel}}(\mathring{M})$ recovers \eqref{eqn: gr Z} from above.
%When $V$ is a product open $U \times [0,\epsilon)$ along the boundary, we find 
%\[
%F_{{\rm rel}}(V) \simeq \clies(0, \Sym(\Omega^*_c(V) \otimes \fg)) \simeq \Sym(\Omega^*_c(V) \otimes \fg),
%\]
%as desired.
